### 2018-11-10 Sabanci_talk/Sabanci_talk.tex
One more slide

\documentclass[xcolor=dvipsnames,t]{beamer}
%\documentclass[xcolor=dvipsnames,handout,t]{beamer}
% use handout in document class to stop transitions

@@

 \begin{frame}{GW Detectors: \red{Interferometers}}
    Two geodesics separated by $\xi^\mu$:
    %\[
    % \frac{D^2 \xi^\alpha}{D\tau^2} = -R^\alpha_{\beta \gamma\delta}\, \xi^\gamma u^\beta u^\delta 
    %\]
    $ \tfrac{d^2 \xi^i}{d\tau^2} = -R^i_{0j0} \xi^j\left(\tfrac{dx^0}{d\tau}\right)^2$ \hfill (detector frame)\\
    %\hspace{4cm} $\Longrightarrow \ddot{\xi^i} = -c^2 R^i_{0j0} \xi^j $ \hfill (detector time)\ \\
    \vspace{-3mm}
    \[
    \hspace{4.5cm} \boxed{\ddot{\xi^i} = \frac{1}{2} \ddot{h}_{ij}^\text{TT} \xi^j} \hspace{2.5cm} \text{(detector time)}
    \]
    %
    %
    \onslide<2->
    {
      GW along $\mathbf{z}$: 
      \[
      h_{ij}^\text{TT} = \left(\begin{array}{cc}
				h_+ & h_\times \\
				h_\times & - h_+
				\end{array}\right) \cos\left(\omega\left( t-\tfrac{z}{c}\right)\right)
      \]
    }
    \onslide<3->
    {
      Consider mirrors at $(0,0)_1, (L,0)_2$ and $(L,L)_3$
      \begin{small}
      \begin{align*}
	s_{12} &= \int_1^2 \tfrac{ds}{dx}dx = (x_2-x_1) \left[ 1 + h_+ \cos(\omega t)\right]^{1/2}\hspace{4cm} \\
				    & \approx L \left[ 1+\tfrac{1}{2} h_+ \cos\omega t \right] \\
      s_{13} &\approx L \left[ 1-\tfrac{1}{2} h_+ \cos\omega t \right]
      \end{align*}
      \end{small}
    }
    %
    \onslide<4->
    {
      \begin{tikzpicture}[overlay,remember picture]
      \node[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-3.4cm)}]current page.center){\todo{Make sure the vid here works}} ;
      %\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.8cm,-2.8cm)}]current page.center) {\animategraphics[loop,controls,height=2.39cm]{12}{LIGO_int-}{0}{30}};
      \end{tikzpicture}
    }
 \end{frame}

@@

\begin{frame}{GW Astronomy in the 2020s}{Advanced LIGO-Virgo}
Detection moment: $t(f=\bar{f})$ such that
%There exists $\bar{f}$ such that
\begin{small}
  \[
    \bar\rho_\text{tot}= \left[\rho_h(f_0^h,\bar{f})\right]^2+\left[\rho_m(f_0^m,\bar{f})\right]^2+\left[\rho_l(f_0^l,\bar{f})\right]^2=\red{15}^2
  \]
\end{small}

@@

\begin{frame}{GW Astronomy in the 2020s}{Advanced LIGO-Virgo}
  Detection moment: $t(f=\bar{f})$ such that
  \begin{small}
    \[
	\bar\rho_\text{tot}= \left[\rho_h(f_0^h,\bar{f})\right]^2+\left[\rho_m(f_0^m,\bar{f})\right]^2+\left[\rho_l(f_0^l,\bar{f})\right]^2=\red{15}^2
    % \textcolor{black}{\bar\rho_\text{tot}=} \onslide<1>\left[\rho_h(f_0^h,\bar{f})\right]^2 \, \textcolor{white}{+}\onslide<2>\left[\rho_m(f_0^m,\bar{f})\right]^2 \, \textcolor{white}{+}\onslide<3->\left[\rho_l(f_0^l,\bar{f})\right]^2\textcolor{white}{=\red{15}^2}
    \]
  \end{small}

@@

\begin{frame}{GW Astronomy in the 2020s}{Advanced LIGO-Virgo}
  Advance \red{warning time}: inspiral time from $\bar{f}$
  \[
    T_\text{AW} = \tau_\text{insp}(\bar{f})
  \]
  \onslide<2->
  {
    Total accumulated SNR over the inspiral
    \begin{footnotesize}
      \[
      \bar{\rho}_\text{F}\equiv\sqrt{\left[{\rho}_h(f_0^h,{f}_\text{ISCO})\right]^2+\left[{\rho}_m(f_0^m,{f}_\text{ISCO})\right]^2+\left[{\rho}_l(f_0^l,{f}_\text{ISCO})\right]^2}
      \]
      \begin{table}[h]
	\centering
	\begin{tabular}{lcccccc}
	  \hline\hline
	  $D\,$(Mpc) & $\bar{f}\,$(Hz) &{}& $T^{0PN}_\text{AW}$(sec) &\hspace{1mm} & $T^{3.5PN}_\text{AW}\text{ (sec)}\hspace{2mm}$& $\bar{\rho}_F$\T \B \\
	  \hline
	  50 & $\approx\,$25.3 & & 84.25 & & 85.86 & 70.3 \\
	  100 & $\approx\,$41.6 & & 22.39 & & 22.86 & 35.2 \\
	  200 & $\approx\,$121 & & 1.291 &\quad & 1.300 & 17.6 \\
	  \hline\hline
	\end{tabular}
      \end{table}
    \end{footnotesize}
  }
%
\onslide<3->$\Longrightarrow$ NO likely FORECASTS  in the 2020s
\begin{tikzpicture}[overlay,remember picture]
  \onslide<1->\node[draw, red,thick,minimum width=2.8cm,minimum height=1.0cm] (b) at (-0.6,5.3){};
\end{tikzpicture}

@@

\begin{frame}{GW Astronomy in the 2030s}{The era of Einstein Telescope}

@@

>>>>

%\documentclass[xcolor=dvipsnames,t]{beamer}
\documentclass[xcolor=dvipsnames,handout,t]{beamer}
% use handout in document class to stop transitions

@@

 \begin{frame}{GW Detectors: \red{Interferometers}}
    Two geodesics separated by $\xi^\mu$:
    %\[
    % \frac{D^2 \xi^\alpha}{D\tau^2} = -R^\alpha_{\beta \gamma\delta}\, \xi^\gamma u^\beta u^\delta 
    %\]
    $ \tfrac{d^2 \xi^i}{d\tau^2} = -R^i_{0j0} \xi^j\left(\tfrac{dx^0}{d\tau}\right)^2$ \hfill (detector frame)\\
    %\hspace{4cm} $\Longrightarrow \ddot{\xi^i} = -c^2 R^i_{0j0} \xi^j $ \hfill (detector time)\ \\
    \vspace{-3mm}
    \[
    \hspace{4.5cm} \boxed{\ddot{\xi^i} = \frac{1}{2} \ddot{h}_{ij}^\text{TT} \xi^j} \hspace{2.5cm} \text{(detector time)}
    \]
    %
    %
    \onslide<2->
    {
      GW along $\mathbf{z}$: 
      \[
      h_{ij}^\text{TT} = \left(\begin{array}{cc}
				h_+ & h_\times \\
				h_\times & - h_+
				\end{array}\right) \cos\left(\omega\left( t-\tfrac{z}{c}\right)\right)
      \]
    }
    \onslide<3->
    {
      Consider mirrors at $(0,0)_1, (L,0)_2$ and $(L,L)_3$
      \begin{small}
      \begin{align*}
	s_{12} &= \int_1^2 \tfrac{ds}{dx}dx = (x_2-x_1) \left[ 1 + h_+ \cos(\omega t)\right]^{1/2}\hspace{4cm} \\
				    & \approx L \left[ 1+\tfrac{1}{2} h_+ \cos\omega t \right] \\
      s_{13} &\approx L \left[ 1-\tfrac{1}{2} h_+ \cos\omega t \right]
      \end{align*}
      \end{small}
    }
    %
    \onslide<4->
    {
      \begin{tikzpicture}[overlay,remember picture]
      \node[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-3.4cm)}]current page.center){\todo{Make sure the vid here works}} ;
      %\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.8cm,-2.8cm)}]current page.center) {\animategraphics[loop,controls,height=2.39cm]{12}{LIGO_int-}{0}{102}};
      \end{tikzpicture}
    }
 \end{frame}

@@

\begin{frame}{GW Astronomy in the 2020s}{Advanced LIGO-Virgo}
Detection moment: $t(f=\bar{f})$ such that
%There exists $\bar{f}$ such that
\begin{small}
  \[
    \bar\rho^2_\text{tot}= \left[\rho_h(f_0^h,\bar{f})\right]^2+\left[\rho_m(f_0^m,\bar{f})\right]^2+\left[\rho_l(f_0^l,\bar{f})\right]^2=\red{15}^2
  \]
\end{small}

@@

\begin{frame}{GW Astronomy in the 2020s}{Advanced LIGO-Virgo}
  Detection moment: $t(f=\bar{f})$ such that
  \begin{small}
    \[
	\bar\rho^2_\text{tot}= \left[\rho_h(f_0^h,\bar{f})\right]^2+\left[\rho_m(f_0^m,\bar{f})\right]^2+\left[\rho_l(f_0^l,\bar{f})\right]^2=\red{15}^2
    % \textcolor{black}{\bar\rho_\text{tot}=} \onslide<1>\left[\rho_h(f_0^h,\bar{f})\right]^2 \, \textcolor{white}{+}\onslide<2>\left[\rho_m(f_0^m,\bar{f})\right]^2 \, \textcolor{white}{+}\onslide<3->\left[\rho_l(f_0^l,\bar{f})\right]^2\textcolor{white}{=\red{15}^2}
    \]
  \end{small}

@@

\begin{frame}{GW Astronomy in the 2020s}{Advanced LIGO-Virgo}
  Advance \red{warning time}: inspiral time from $\bar{f}$
  \[
    T_\text{AW} = \tau_\text{insp}(\bar{f})
  \]
  \onslide<2->
  {
    Total accumulated SNR over the inspiral
    \begin{footnotesize}
      \[
      \bar{\rho}_\text{F}\equiv\sqrt{\left[{\rho}_h(f_0^h,{f}_\text{ISCO})\right]^2+\left[{\rho}_m(f_0^m,{f}_\text{ISCO})\right]^2+\left[{\rho}_l(f_0^l,{f}_\text{ISCO})\right]^2}
      \]
      \begin{table}[h]
	\centering
	\begin{tabular}{lcccccc}
	  \hline\hline
	  $D\,$(Mpc) & $\bar{f}\,$(Hz) &{}& $T^\text{0PN}_\text{AW}$(sec) &\hspace{1mm} & $T^\text{3.5PN}_\text{AW}\text{ (sec)}\hspace{2mm}$& $\bar{\rho}_F$\T \B \\
	  \hline
	  50 & $\approx\,$25.3 & & 84.25 & & 85.86 & 70.3 \\
	  100 & $\approx\,$41.6 & & 22.39 & & 22.86 & 35.2 \\
	  200 & $\approx\,$121 & & 1.291 &\quad & 1.300 & 17.6 \\
	  \hline\hline
	\end{tabular}
      \end{table}
    \end{footnotesize}
  }
%
\onslide<3->$\Longrightarrow$ NO likely FORECASTS  in the 2020s
\begin{tikzpicture}[overlay,remember picture]
  \onslide<1->\node[draw, red,thick,minimum width=2.8cm,minimum height=1.0cm] (b) at (-0.7,5.3){};
\end{tikzpicture}

@@

\begin{frame}{GW Astronomy in the 2030s}{The era of Einstein Telescope}
 One detector, \red{three V}-IFOs, $60^\circ$ 10\,km arms.\\
 Underground,cryogenic, \bl{xylophone} (high, low-frequency modes)\\
 \vspace{1mm}
 Cosmological range $\Rightarrow$ sky-averaged,\red{red}-shifted strain and SNR
 \begin{footnotesize}
 \begin{align*} 
  \tilde{H}_\text{ET}(f) &= \f{3}{5}A h_0 \red{(1+z)^{-1}} f^{-7/6}\\
  \bar\rho_{\text{ET}}(f_0,f)&\equiv \f{6}{5}A h_0\, \red{(1+z)^{-1/6}}\left[\int_{f_0}^{f} d f'\, \f{f'^{-7/3}}{S^\text{ET}_n(f')}\right]^{1/2}
 \end{align*} 
 \end{footnotesize}
Consider BNS at \\
$$ D=\{100,200, 400, 600\}\,\text{Mpc} \Longrightarrow z=\{0.022, 0.044, 0.085, 0.12\}$$
$\Omega_\Lambda = 0.6911, \Omega_m = 0.3089, H_0 = 67.74\,$km\,s$^{-1}\,$Mpc$^{-1}$

@@

  One detector, \red{three V}-IFOs, $60^\circ$ 10\,km arms.\\
 Underground,cryogenic, \blue{xylophone} (high, low-frequency modes)\\

 Cosmological range $\Rightarrow$ sky-averaged,\red{red}-shifted strain and SNR
 \begin{footnotesize}
 \begin{align*} 
  \tilde{H}_\text{ET}(f) &= \f{3}{5}A h_0 \red{(1+z)^{-1}} f^{-7/6}\\
  \bar\rho_{\text{ET}}(f_0,f)&\equiv \f{6}{5}A h_0\, \red{(1+z)^{-1/6}}\left[\int_{f_0}^{f} d f'\, \f{f'^{-7/3}}{S^\text{ET}_n(f')}\right]^{1/2}
 \end{align*} 
 \end{footnotesize}
